In the digital age, the concept of decentralisation has emerged as a transformation paradigm, reshaping the way we understand and interact with systems and networks~\cite{Tverdokhlib.2022}. Decentralised platforms, at their core, are systems where components, be it data, resources, or operations, are not controlled or managed by a single, central entity. Instead, they are distributed across multiple nodes or participants, each having equal authority and autonomy. This contrasts sharply with traditional centralised systems, where a single entity or a group of entities holds the power and control. In the following chapter we will introduce the core concepts behind decentralised platforms and showcase how data privacy can be handled in a system without a central authority.


\subsection{Introduction to Decentralised Platforms}

One of the primary characteristics of decentralised platforms is the absence of a central point of control. This means that no single entity has the authority to make unilateral decisions or changes without consensus from the majority of the network's participants~\cite{SEFRAOUI.2022}. This leads to enhanced security, as the absence of a single point of failure makes the system more resilient to attacks~\cite{Maffiola.2022}. Additionally, decentralised platforms often employ cryptographic techniques to ensure data integrity, privacy, and authentication. This ensures that transactions and interactions on the platform are secure, verifiable, and tamper-proof~\cite{SEFRAOUI.2022}.

Comparing decentralised platforms with centralised systems reveals strong differences in their operational philosophies and outcomes~\cite{Maffiola.2022}. Centralised systems, such as traditional databases or web servers, are controlled by a single entity. This central authority has the power to dictate rules, make changes, grant or deny access, and is also the primary custodian of the data~\cite{Maffiola.2022}. While this centralisation can lead to efficiencies in terms of decision-making and streamlined operations, it also presents vulnerabilities. A single point of failure in a centralised system can lead to the entire system's collapse~\cite{Maffiola.2022}. Moreover, centralisation often results in data silos, where information is trapped within one part of the system, inaccessible to others.

On the other hand, decentralised platforms operate on the principles of democracy and transparency~\cite{SEFRAOUI.2022}. Decisions are made based on consensus algorithms, ensuring that no single participant can dominate or manipulate the system. This democratisation of control can lead to enhanced trust among users, as they are assured that the platform operates in a fair and transparent manner~\cite{Hasan.2022}. Moreover, data in decentralised systems is typically stored across multiple nodes, ensuring redundancy and resilience~\cite{Hasan.2022}. Even if one or more nodes fail, the system can continue to operate seamlessly.

The potential benefits of decentralised platforms are manifold~\cite{Hasan.2022}. Firstly, they offer enhanced security and resilience due to their distributed nature. The risk of system-wide failures or attacks is significantly reduced~\cite{Maffiola.2022}. Secondly, they promote transparency and trust among users, as decisions are made collectively and openly~\cite{Hasan.2022}. This can lead to increased user adoption and loyalty. Furthermore, decentralised platforms can lead to innovations in peer-to-peer transactions, smart contracts, and decentralised applications, opening up new avenues for business and social interactions.

However, like any transformative technology, decentralised platforms come with their set of challenges~\cite{Hasan.2022}. The lack of a central authority can sometimes lead to slower decision-making, as achieving consensus can be time-consuming. Additionally, the technology underpinning decentralised platforms, such as blockchain, is still maturing, leading to scalability and performance issues~\cite{Hasan.2022}. Interoperability between different decentralised platforms is also a concern, as it can hinder seamless integration and communication.

In conclusion, decentralised platforms represent a paradigm shift in the way we design and interact with digital systems~\cite{Tverdokhlib.2022}. While they offer numerous advantages in terms of security, transparency, and innovation, they also present challenges that need to be addressed~\cite{Hasan.2022}. As the technology matures and evolves, it will be fascinating to witness the transformative impact of decentralised platforms on various sectors of the economy and society at large.


\subsection{Data Privacy: Definition and Importance}
In the digital age, where vast amounts of data are generated and exchanged every second, understanding the nuances of data privacy becomes paramount. Data privacy, at its core, refers to the right of individuals to control or influence what information about them is collected and how it is used. It encompasses the practices, safeguards, and binding rules put in place to protect personal information and ensure that individuals remain in control of it~\cite{Covert.2020}. This concept is crucial for several reasons.

Firstly, data privacy is intrinsically linked to personal autonomy and dignity. In a world where personal data can reveal intimate details about an individual's life, preferences, and habits, ensuring that such information is not misused or mishandled is vital~\cite{Covert.2020}. Without robust data privacy measures, individuals may feel violated, leading to a loss of trust in digital systems and platforms.

Secondly, data privacy is essential for safeguarding fundamental human rights, such as the right to freedom of expression and the right to seek and receive information. When individuals are unsure about the privacy of their data, they may hesitate to express their views or access information freely, fearing surveillance or repercussions.

Furthermore, in the context of businesses and services, data privacy is crucial for maintaining consumer trust. Companies that fail to protect user data or misuse it can face significant reputational damage, legal consequences, and financial losses~\cite{Li.2019}. In sectors like decentralised ride-sharing, where users share location data, payment details, and personal preferences, ensuring data privacy can be the difference between a successful platform and one that users abandon due to trust issues~\cite{Li.2019}.

While data privacy is a critical concept, it is essential to distinguish it from related terms like data security and data protection, as they are often used interchangeably but have distinct meanings.

Data security refers to the protective measures and technologies used to safeguard data from unauthorised access, breaches, or theft. It focuses on defending data from malicious threats, be it hackers, malware, or other cyber-attacks. For instance, using encryption to secure data or firewalls to prevent unauthorised access are examples of data security practices.

On the other hand, data protection is a broader concept that encompasses both data privacy and data security. It refers to the policies, procedures, and legal measures designed to ensure that data is collected, stored, and used in a way that respects individual rights and complies with relevant laws and regulations~\cite{Covert.2020}. Data protection laws, such as the General Data Protection Regulation (GDPR) in the European Union, set out the principles and guidelines that organisations must follow when handling personal data.

In conclusion, data privacy is the right of individuals to control their personal information and its usage~\cite{Covert.2020}. Its importance cannot be overstated, given its implications for personal autonomy, human rights, and business trust~\cite{Li.2019}. While closely related, it differs from data security, which focuses on defending data from threats, and data protection, which encompasses the overarching policies and laws governing data handling~\cite{Covert.2020}. As we continue to integrate digital platforms into every facet of our lives, understanding and prioritising data privacy will remain of paramount importance.

\subsection{Mechanisms of Data Privacy in decentralised Blockchain Systems}
Decentralised blockchain systems have emerged as a revolutionary technology, offering the promise of transparency, immutability, and disintermediation. However, the very nature of public blockchains, which are open and transparent, poses significant privacy challenges. Every transaction and its associated data are visible to anyone who accesses the blockchain, leading to potential privacy breaches and exposure of sensitive information.

Encryption plays a pivotal role in addressing these challenges. At its core, encryption involves converting data into a code to prevent unauthorised access. In the context of blockchains, public key and private key encryption is widely used. A public key, visible to everyone, is used to encrypt data, while a private key, known only to the owner, is used to decrypt it. This ensures that only the intended recipient can access the information. Furthermore, end-to-end encryption ensures that data remains encrypted during its entire journey from the sender to the recipient, preventing potential eavesdroppers from accessing the information during transmission.

Another advanced cryptographic technique employed in blockchains is zero-knowledge proofs (ZKPs). ZKPs allow one party to prove to another that a statement is true without revealing any specific information about the statement itself. For instance, in a transaction, a user can prove they have sufficient funds without revealing the exact amount. This ensures transaction validity while preserving user privacy.

Homomorphic encryption offers another layer of privacy. It allows computations to be performed on encrypted data without first decrypting it. The result, when decrypted, remains accurate. This means that blockchain systems can process transactions and maintain data integrity without exposing the actual data, a boon for privacy-centric applications.

Secure multi-party computation (SMPC) is a cryptographic protocol that allows multiple parties to jointly compute a function over their inputs while keeping those inputs private. In the context of blockchains, SMPC can enable decentralised applications to function without revealing user data to other participants, ensuring data privacy and security.

While public blockchains offer unparalleled transparency, they might not be suitable for all applications, especially those requiring higher levels of privacy. Private and consortium blockchains emerge as alternatives in such scenarios. Private blockchains restrict participation to selected entities, while consortium blockchains involve multiple organisations governing the network. Both these types limit data visibility to only authorised participants, enhancing data privacy.

Another approach to establish  an encrypted connection over a public network is the Diffie-Hellman Key Exchange. The Diffie-Hellman Key Exchange, introduced by Whitfield Diffie and Martin Hellman in 1976, is a cryptographic protocol that allows two parties to independently generate a shared secret key over an insecure communication channel. The protocol is based on the mathematical properties of modular arithmetic and discrete logarithm problems. Specifically, given a prime number \( p \) and a base \( g \) (where \( g \) is a primitive root modulo \( p \)), each party selects a private key and computes a public key. The public keys are then exchanged, and each party uses the other's public key along with their own private key to compute the shared secret. The security of the protocol relies on the difficulty of the discrete logarithm problem: while it is computationally easy to generate the public key from the private key, the reverse operation is considered infeasible with current technology when large prime numbers are used.

Off-chain storage is another solution to the privacy challenges. Instead of storing all data on the blockchain, only essential information is kept on-chain, while the rest is stored off-chain in secure databases. This reduces the amount of data exposed on the public ledger, ensuring privacy.

Lastly, layer 2 solutions, built on top of the primary blockchain, offer scalability and privacy improvements. By processing transactions off the main chain and only settling the final state on-chain, these solutions can ensure faster transactions and enhanced privacy.

In conclusion, while decentralised blockchain systems present certain inherent privacy challenges, a combination of cryptographic techniques and architectural solutions can effectively address these concerns, paving the way for a more secure and private decentralised future.

\subsection{Regulatory and Legal Challenges in Decentralised Blockchain Systems}
Decentralised blockchain systems, while revolutionary in their potential to disrupt traditional centralized models, face a myriad of regulatory and legal challenges. At the forefront of these challenges is the General Data Protection Regulation (GDPR), a regulation that has reshaped the landscape of data protection in the European Union and has significant implications for decentralised systems.

The GDPR emphasises the rights of individuals over their personal data, including the right to access, rectify, and erase their data. In a centralised system, complying with these rights is straightforward, as there's a single entity controlling the data. However, in decentralised blockchain systems, data is distributed across a network of nodes, making modifications or deletions challenging~\cite{Schwerin.2018}. Once data is added to the blockchain, it becomes immutable, meaning it cannot be altered or deleted. This immutability clashes with the GDPR's "right to be forgotten," where individuals can request their data to be erased~\cite{BelenSaglam.}. Thus, blockchain developers and operators must tread carefully, ensuring that personal data is either kept off-chain or encrypted in a way that it can be rendered inaccessible if required.

Beyond the GDPR, other regional data protection regulations further complicate the landscape. For instance, California's Consumer Privacy Act (CCPA) and Brazil's General Data Protection Law (LGPD) have their own sets of requirements, some of which may conflict with the decentralised nature of blockchains. These regulations, while primarily designed to protect consumers, can pose challenges for decentralised systems that operate across multiple jurisdictions. Ensuring compliance with a patchwork of regional regulations requires a deep understanding of each jurisdiction's nuances and a flexible system architecture that can adapt to diverse requirements.

Legal challenges in decentralised blockchain systems are not limited to data protection. The very nature of decentralisation means there's often no single entity to hold accountable, making it difficult to enforce regulations or resolve disputes. For instance, in a decentralised ride-sharing platform, if a dispute arises between a driver and a passenger, the absence of a central authority like traditional ride-sharing companies complicates resolution. Moreover, the pseudonymous nature of blockchain transactions can pose challenges in identifying parties in legal proceedings.

However, the decentralised community is not without potential solutions. One approach is the use of ''smart contracts'' – self-executing contracts with the terms directly written into code. These can automate and streamline compliance processes, ensuring that transactions adhere to regional regulations. Additionally, off-chain storage solutions can be employed to store sensitive personal data, linking it to the blockchain through secure cryptographic hashes. This ensures data can be modified or deleted as required, without compromising the immutability of the blockchain~\cite{Schwerin.2018}.

In conclusion, while decentralised blockchain systems offer transformative potential, they must navigate a complex web of regulatory and legal challenges. By understanding these challenges and innovating solutions that respect both the spirit of decentralisation and the need for regulatory compliance, blockchain systems can pave the way for a more decentralised and equitable digital future.
