Having delved into the intricate details of the current research landscape surrounding decentralized ride-sharing platforms, we now embark on the journey of constructing our unique platform. This endeavor is not merely a replication of existing systems but aims to set a benchmark that encapsulates the zenith of academic literature. Moreover, it seeks to introduce enhancements that surpass the capabilities of current methodologies.

The platform we propose stands out as a pioneering effort in this domain. It is the first of its kind to holistically address all the pivotal attributes of a ride-sharing platform that were discerned through rigorous literature research. These attributes encompass Blockchain Utilisation, Transparency, User and Provider Interaction Protocols, Payments and Service Fees, Privacy and Anonymity, Security and Resilience, Trust Mechanisms, Off-Chain Edge Cases, and Prototypical Realization.

In this chapter, we will delve deeply into the design intricacies of our proposed platform. We will elucidate the conceptual framework, interaction protocols, trust mechanisms, and privacy measures that form the bedrock of this innovative solution. Through this exploration, we aim to provide a comprehensive blueprint for a decentralized ride-sharing platform that not only meets but exceeds the expectations set by the current academic and industry standards.

For convenience the proposed platform will from now on be called GETACAR. The name was chosen for its ability to describe the core offering of the platform, to get-a-car ride, while also being short, recognisable and easy to remember.

(The name also sounds phonetically similar to the title of the 1998 science fiction movie Gattaca, staring Ethan Hawke, Uma Thurman and Jude Law, that the author of this paper quite enjoyed)